Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-03-06 ongoing/report/1_introduction.tex
Correct delimiters usage

\m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} (a)} and \m {\MF {Im} (a)}, respectively, thus \m {a =\MF {Re} (a) + i \MF {Im} (a)}

@@

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} (N)}.
We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} (M,N)}, and its role as linear transformation is understood.
Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
Slightly abusing notation, we denote as \m {\V {a} (n)} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} (m,n)} the \m {(m,n)}-entry of \m {\V {A}}
Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.

Denote as \m {\MB {P} (X)} the probability, and \m {\MB {E} (X)} the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

Round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments.

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det (I +\RM {SNR})}, but that knowledge is hardly always available.
What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det (I +\RM {SNR})}.

@@

We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} (N_m)}.

\Result
{Definition}
{
Suppose \m {\M {A} \in \MB {M}_{\MB {K}} (N_m, N_p)}.
Let \m {\MC {T} \subset T \RB {N_p}}.
Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
}

\Result
{Definition}
{
\m {x \in \MB {V}_{\MB {K}} (N_m)} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
%
\Disp { 
\NC x_{T(N) -\MC {A}}
=\NC \V {0} \NR
}
with
\Disp { 
\NC \# \MC {A} \leq s. \NR
}
That is, only at most \m {s} components of \m {x} is nonzero.
}

\Result
{Program}
{
Let \m {P \in \MB {M}_\MB {K} (N_m, N_p)} and \m {y \in \MB {V}_\MB {K} (N_p)} be given.
Find \m {h \in \MB {V}_\MB {K} (N_p)} with
%
\Disp {
\NC
h
= \NC \startcases
\NC \Min {h'}
\quad \MC \VNm {h'} _1 \NR[+]
\NC \RM {subject} \; \RM {to}
\quad \MC P h' =y \NR
\stopcases \NR
}
}

@@

\Result
{Definition}
{
Consider \m {P \in \MB {M}_{\MB {K}} (N_m, N_p)}, with unity-\m {\ell_2}-norm columns.
For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} (N_p)}, for all \m {\MC {T} \subset T(N_m)} with \m {\#\{\MC {T} \} \leq s},
%
\Disp {
\NC \NC (1-\d_s) \VNm {V {x}}^2 \NR
\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
\NC \leq \NC (1+\d_s) \VNm {\V {x}} _2^2 \NR[+]
}
}

@@

\Result
{Program}
{
Let \m {\M {P} \in \MB {V}_\MB {R} (N_m, N_p)} and \m {\V {y} \in \MB {V}_\MB {R} (N_m)} be given.
Find \m {\V {h} \in \MB {V}_\MB {R} (N_m)} by
%

\Disp {
\NC \V {h}
= \NC \startcases
\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H (\M {P} \V {h} -\V {y})} _\infty \leq \gamma \NR
\stopcases \NR
}
}

@@

\Result
{Theorem}
{
Let each entry of random matrix \m {P \in \MB {M}_\MB {K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
Then, with \m {0 <\epsilon <1},
%
\Disp {
\NC \NC \MB {P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2) \NR
\NC \leq \NC 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) ) \NR
}
}

@@

To explain the idea, consider a linear time-invariant channel that \m {y(t) =(x \star h)(t) + z(t)}, where \m {h(t)} is the channel's impulse response, \m {y(t)} is the output, and, for each time index, \m {x(t)} is i.i.d.\ Rademacher, and \m {z(t)} is i.i.d.\ Gaussian.
Simply assuming \m {h} has sparse support, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
Then Bajwa et.\ al.\ was able to show that, \m {X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

@@

Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} (N_p)}, \m {\V {h} \in \MB {V}_\MB {K} (N_s)}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
If
\Disp {
\NC \V {y} =\M {P} \V {h}, \NR
}
that is, the noiseless, real-number case.
We pick up the columns of \m {\M {P}} greedily, hoping to correspond to the support of \m {\V {h}}, thus recovering the original signal.

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \m {0 <\d <1},
%
\Disp {
\NC M \geq 16s \log (N/\d) \NR
}
%
Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
}

@@

\Result
{Definition}
{
Define \m {\RM {vec} (\M {A}) \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} (N,M)}.
}

\Result
{Definition.}
{
For \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)} and \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)}
Define the Kronecker product \m {\RM {vec} (A) \in \MB {K}^{nm}} 
}

With (), scholars often exploit the relation
%
\Disp {
\NC \RM {vec} (Y)
=\big[ (F^\H) \otimes W \big] \RM {vec} (\M {H}) \NR
}
%

>>>>

First of all, round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments, for better clarity.

\m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} \SB {a}} and \m {\MF {Im} \SB {a}}, respectively, thus \m {a =\MF {Re} \SB {a} + i \MF {Im} \SB {a}}

@@

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} \SB {N}}.
We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} \SB {M,N}}, and its role as linear transformation is understood.
Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {\DB {m,n}}-entry of \m {\V {A}}
Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.

Denote as \m {\MB {P} \SB {X}} the probability, and \m {\MB {E} \SB {X}} the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\RM {SNR}}}, but that knowledge is hardly always available.
What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\RM {SNR}}}.

@@

We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} \SB {N_m}}.

\Result
{Definition}
{
Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
Let \m {\MC {T} \subset T \RB {N_p}}.
Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
}

\Result
{Definition}
{
\m {x \in \MB {V}_{\MB {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
%
\Disp { 
\NC x_{T\SB {N} -\MC {A}}
=\NC \V {0} \NR
}
with
\Disp { 
\NC \# \MC {A} \leq s. \NR
}
That is, only at most \m {s} components of \m {x} is nonzero.
}

\Result
{Program}
{
Let \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} and \m {y \in \MB {V}_\MB {K} \SB {N_p}} be given.
Find \m {h \in \MB {V}_\MB {K} \SB {N_p}} with
%
\Disp {
\NC
h
= \NC \startcases
\NC \Min {h'}
\quad \MC \VNm {h'} _1 \NR[+]
\NC \RM {subject} \; \RM {to}
\quad \MC P h' =y \NR
\stopcases \NR
}
}

@@

\Result
{Definition}
{
Consider \m {P \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N_p}}, for all \m {\MC {T} \subset T\SB {N_m}} with \m {\#\{\MC {T} \} \leq s},
%
\Disp {
\NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
}
}

@@

\Result
{Program}
{
Let \m {\M {P} \in \MB {V}_\MB {R} \SB {N_m, N_p}} and \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}} be given.
Find \m {\V {h} \in \MB {V}_\MB {R} \SB {N_m}} by
%

\Disp {
\NC \V {h}
= \NC \startcases
\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
\stopcases \NR
}
}

@@

\Result
{Theorem}
{
Let each entry of random matrix \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
Then, with \m {0 <\epsilon <1},
%
\Disp {
\NC \NC \MB {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2} \NR
\NC \leq \NC 2 \exp \SB {-n \RB {\epsilon^2/4 -\epsilon^3/6} } \NR
}
}

@@

To explain the idea, consider a linear time-invariant channel that \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and, for each time index, \m {x\SB {t}} is i.i.d.\ Rademacher, and \m {z\SB {t}} is i.i.d.\ Gaussian.
Simply assuming \m {h} has sparse support, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
Then Bajwa et.\ al.\ was able to show that, \m {X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

@@

Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} \SB {N_p}}, \m {\V {h} \in \MB {V}_\MB {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
If
\Disp {
\NC \V {y} =\M {P} \V {h}, \NR
}
that is, the noiseless, real-number case.
We pick up the columns of \m {\M {P}} greedily, hoping to correspond to the support of \m {\V {h}}, thus recovering the original signal.

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \m {0 <\d <1},
%
\Disp {
\NC M \geq 16s \log \RB {N/\d} \NR
}
%
Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
}

@@

\Result
{Definition}
{
Define \m {\RM {vec} \SB {\M {A}} \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N,M}}.
}

\Result
{Definition.}
{
For \m {\RM {vec} \SB {A} \in \MB {M}_{\MB {K}} \SB {N,M}} and \m {\RM {vec} \SB {A} \in \MB {M}_{\MB {K}} \SB {N,M}}
Define the Kronecker product \m {\RM {vec} \SB {A} \in \MB {K}^{nm}} 
}

With (), scholars often exploit the relation
%
\Disp {
\NC \RM {vec} \SB {Y}
=\big[ \RB {F^\H} \otimes W \big] \RM {vec} \RB {\M {H}} \NR
}
%
